\documentclass[a4paper]{article}

\usepackage[english]{babel} 
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{pst-all}
\usepackage{caption}
\usepackage{float}
\usepackage{fullpage}

\title{WORQ 19}

\author{Theo Makler}

\date{\today}

\begin{document}
\maketitle

\section{Problem B}
A trapezoid with three sides that are 1 unit long and one side that is 2 units long creates a quadrilateral with exactly 3 congruent sides.

When I started this problem, I knew that the quadrilateral had to be a trapezoid because if the figure has 3 congruent sides, then one side must be either shorter or longer. I made a quadrilateral with the top and sides all one unit long:

\begin{figure}[h]
\centering
\begin{pspicture}(.25,.25)(.25,.25)
\psset{unit=1}
\psdot(-.5,.85)
\psdot(.5,.85)
\psdot(-1,0)
\psdot(1,0)
\psline{-}(-.5,.85)(.5,.85)
\psline{-}(-1,0)(1,0)
\psline{-}(-.5,.85)(-1,0)
\psline{-}(.5,.85)(1,0)
\end{pspicture}
\end{figure}

I made the bottom base have a length of 2 because I know that 2 is greater than one:

\begin{figure}[h]
\centering
\begin{pspicture}(.25,1.5)(.25,.25)
\psset{unit=1.5}
\psdot(-.5,.85)
\psdot(.5,.85)
\psdot(-1,0)
\psdot(1,0)
\psline{-}(-.5,.85)(.5,.85)
\psline{-}(-1,0)(1,0)
\psline{-}(-.5,.85)(-1,0)
\psline{-}(.5,.85)(1,0)
\psline[linestyle=dashed,dash=3pt 2pt](-.5,.85)(-.5,0)
\psline[linestyle=dashed,dash=3pt 2pt](.5,.85)(.5,0)
\rput(-1,.5){\psframebox*{$1$}}
\rput(1,.5){\psframebox*{$1$}}
\rput(0,1){\psframebox*{$1$}}
\rput(0,-.15){\psframebox*{$2$}}
\rput(0,1.2){\psframebox*{$$}}
\rput(0,1.2){\psframebox*{$$}}
\end{pspicture}
\end{figure}

As you can see, this is a quadrilateral with exactly 3 congruent sides.

\section{Problem C}

The equation $-\sqrt{x^6}=\frac{3^4+3^3+540}{3}$ makes $x=-6$, the equation $x=\frac{x}{3}\times \frac{\sqrt{421201}}{649}$ has no solutions, and the equation $\frac{\sqrt{266256}}{\sqrt{931225}}\times\frac{\sqrt{931225}}{\sqrt{266256}}=\frac{(x+1)(x-1)}{x^2-1}$ has infinite solutions.

We can prove these problems by simplifying them. For the first one, we can just substitute $x$ for $-6$ like this:

\begin{align*}
-\sqrt{x^6}&=\frac{3^4+3^3+540}{3} \\
-\sqrt{-6^6}&=\frac{3^4+3^3+540}{3} \\
-(-216)&=\frac{648}{3} \\
216&=216 
\end{align*}

As this shows, the problem $-\sqrt{x^6}=-\frac{3^4+3^3+540}{3}$ makes $x=-6$ We can simplify the second problem to prove it has no solutions:

\begin{align*}
x&=\frac{x}{3}\times \frac{\sqrt{421201}}{649} \\
x&=\frac{x}{3}\times\frac{649}{649}\\
x&\ne\frac{x}{3} 
\end{align*}

As this shows, the problem $x=\frac{x}{3}\times \frac{\sqrt{421201}}{649}$ does not have any solutions. Finally, the last problem has infinite solutions:

\begin{align*}
\frac{\sqrt{266256}}{\sqrt{931225}}\times\frac{\sqrt{931225}}{\sqrt{266256}}&=\frac{(x+1)(x-1)}{x^2-1} \\
1&=\frac{x^2-1}{x^2-1}\\
1&=1 
\end{align*}

As these equations show, the problem $\frac{\sqrt{266256}}{\sqrt{931225}}\times\frac{\sqrt{931225}}{\sqrt{266256}}=\frac{(x+1)(x-1)}{x^2-1}$ has infinite solutions.

\section{Problem D}

The points $(1,1)$, $(4,1)$, $(3,2)$, and $(2,2)$ make an isosceles trapezoid.

The definition of an isosceles trapezoid by Wikipedia is "In Euclidean geometry, an isosceles trapezoid (isosceles trapezium in British English) is a convex quadrilateral with a line of symmetry bisecting one pair of opposite sides, making it automatically a trapezoid." This means that the trapezoid must be symetrical. I first plotted my points on a graph like this: 








\end{document}